Two-Dimensional Vesicle Hydrodynamics from Hydrophobic Attraction Potential

### 2021-09-28 doc/main_jfm.tex
yny abstract 2

\begin{abstract}
  We develop a new model, to our knowledge,  for the many-body  hydrodynamics of amphiphilic 
  Janus particles suspended in a viscous background flow. 
  The Janus particles interact with each other directly through a hydrophobic attraction potential (HAP)
  that has been shown to model lipid bilayer membranes. In addition they also interaction with each other indirectly through the hydrodynamic interactions.
  We adopt an efficient integral equation method for solving the screened
  Laplace equation (for the HAP) and the mobility of Janus particles in a viscous fluid. 
  Both the hydrophobic and hydrodynamic interactions between near
  touched boundaries are accurately captured within the integral formulation. Under a linear shear flow,  we observe the tank-treading deformation
  in a two-dimensional vesicle made of Janus particles for various values of the shear rate.
  The results yield measurements 
  of inter-monolayer friction and membrane permeability. Large shear rates lead to membrane rupture. 
  The simulations studies include a vesicle in parabolic flow and vesicle-vesicle 
  interactions in shear and extensional flows. We find that the hydrodynamics of a  vesicle assembled from Janus particles is similar to that of
  a lipid bilayer vesicle often described by the Helfrich free energy of an inextensible elastic membrane.
%    We develop a new model, to our knowledge,  for the hydrodynamics of amphiphilic particles in background flows. 
%  In this work, we study the dynamics of many-body systems immersed in a
%  viscous fluid with a specified interparticle force. In particular, we
%  apply a hydrophobic attraction potential (HAP) using a Janus type
%  granular system to model lipid bilayer membranes. Coupling with an
%  efficient integral equation method for rigid bodies in Stokes flow and
%  a previous developed HAP solver, the deformations of a two-dimensional
%  vesicle such as tank-treading motion and membrane ruptures can be
%  observed under different values of the shear rate. Moreover, an
%  efficient integral equation method is adopted for solving the screened
%  Laplace equation and the mobility problem where it can accurately
%  calculate hydrophobic and hydrodynamic interactions between near
%  touched boundaries.
\end{abstract}

>>>>

\begin{abstract}
  We develop a new model, to our knowledge,  for the many-body  hydrodynamics of amphiphilic 
  Janus particles suspended in a viscous background flow. 
  The Janus particles interact with each other directly through a hydrophobic attraction potential (HAP)
  that has been shown to model lipid bilayer membranes. In addition they also interact with each other indirectly through the hydrodynamic interactions.
  We adopt an efficient integral equation method for solving the screened
  Laplace equation (for the HAP) and the mobility of Janus particles in a viscous fluid. 
  Both the hydrophobic and hydrodynamic interactions between near
  touched boundaries are accurately captured within the integral formulation. Under a linear shear flow,  we observe the tank-treading deformation
  in a two-dimensional vesicle made of Janus particles for various values of the shear rate.
  The results yield measurements 
  of inter-monolayer friction and membrane permeability. Large shear rates lead to membrane rupture. 
  The simulations studies include a vesicle in parabolic flow and vesicle-vesicle 
  interactions in shear and extensional flows. We find that the hydrodynamics of a  vesicle assembled from Janus particles
replicates the dynamics of an inextensible elastic vesicle.
%    We develop a new model, to our knowledge,  for the hydrodynamics of amphiphilic particles in background flows. 
%  In this work, we study the dynamics of many-body systems immersed in a
%  viscous fluid with a specified interparticle force. In particular, we
%  apply a hydrophobic attraction potential (HAP) using a Janus type
%  granular system to model lipid bilayer membranes. Coupling with an
%  efficient integral equation method for rigid bodies in Stokes flow and
%  a previous developed HAP solver, the deformations of a two-dimensional
%  vesicle such as tank-treading motion and membrane ruptures can be
%  observed under different values of the shear rate. Moreover, an
%  efficient integral equation method is adopted for solving the screened
%  Laplace equation and the mobility problem where it can accurately
%  calculate hydrophobic and hydrodynamic interactions between near
%  touched boundaries.
\end{abstract}
